---
title: "STATS 503 Group Project"
subtitle: "How will the Trump tweets affect daily stock prices?"
author: "Group 14 - Xiaolin Cao, Ting-Wei Lin, Ming-Chen Lu, Suzy McTaggart"
date: "`r format.Date(Sys.Date(), '%B %d, %Y')`"
geometry: "left = 2cm, right = 2cm, top = 2cm, bottom = 2cm"
output: 
  html_document:
    code_folding: hide
    toc: yes
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(message = FALSE, echo = TRUE, warning = FALSE, 
                      result = "asis", cache = TRUE)
```

```{r tweets}
# Library
library(tidyverse)
theme_set(theme_bw())

# Read in data
setwd("/Users/Amy/Desktop/Stat503/Group_proj")
tweets = read.csv("./data/trumptweets.csv")
col = c("content", "date", "retweets", "favorites")
tweets = tweets[col]
tweets$day = as.Date(tweets$date, format = "%Y-%m-%d")
new_id = data.frame(day = unique(tweets$day), new_id = 1:length(unique(tweets$day)))
tweets = inner_join(new_id, tweets, by = "day")
```

# Data Exploration

1. What time of day the tweets occur?

```{r , dependson = "tweets"}
library(lubridate)
library(scales)
tweets %>%
  count(hour = hour(date)) %>%
  mutate(percent = n / sum(n)) %>%
  ggplot(aes(x = hour, y = percent)) +
  geom_line() +
  scale_y_continuous(labels = percent_format()) +
  labs(x = "Hour of day (EST)",
       y = "% of tweets")
```

# Data Preprocessing
Difference in the *content*?

Dividing into individual words using the `unnest_tokens` function (see [this vignette](https://cran.r-project.org/web/packages/tidytext/vignettes/tidytext.html) for more), and removing some common "stopwords"[^regex].

```{r tweet_words, dependson = "tweets"}
library(tidytext)

reg <- "([^A-Za-z\\d#@']|'(?![A-Za-z\\d#@]))"
tweets_words = tweets %>%
  mutate(
    text = str_remove_all(content,
                          "https?://[A-Za-z\\d///.]+|[//\\d]+|\"+|/<+|/>+|//.+&amp+")
    ) %>%
  unnest_tokens(word, text, token = "regex", pattern = reg) %>%
  filter(!word %in% stop_words$word, str_detect(word, "[a-z]"))
```

What were the most common words in Trump's tweets overall?

```{r tweets_words_plot, dependson = "tweets_words", fig.height = 6, fig.width = 8, echo = FALSE}
tweets_words %>%
  count(word, sort = TRUE) %>%
  head(25) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_bar(stat = "identity") +
  ylab("Occurrences") + coord_flip()
```

A few observations:

# References
- Sentiment analysis of Trump's tweets with R https://blog.revolutionanalytics.com/2016/08/sentiment-analysis-of-trumps-tweets-with-r.html

- https://github.com/dgrtwo/dgrtwo.github.com/blob/master/_R/2016-08-09-trump-tweets.Rmd



